Using occupancy theory and Bayesian models to estimate otter populations in southeastern Minnesota

### 2010-03-02 Presentation/Presentation.tex
fixed a mistake
Being anal, removing the duplicate model diagram.

\begin{document}
	{
	\usebackgroundtemplate{\includegraphics[width=\paperwidth]{ottertracks1.jpg}}

\begin{frame}
	\titlepage
\end{frame}
}
\begin{frame}
	\tableofcontents[pausesections]
\end{frame}

@@

{
	\usebackgroundtemplate{\includegraphics[width=\paperwidth]{SnowTracks12.jpg}}
	\begin{frame}{}
	\end{frame}
}

{
	\usebackgroundtemplate{\includegraphics[width=\paperwidth]{SNOWTRACKS9.jpg}}
	\begin{frame}
	\end{frame}
}

\begin{frame}{Issues related to data}
	\begin{itemize}
		\item Tracks near plot boundary can be assigned to different plots
		\item Track in one site means more likely to be track in neighboring site- not independent
	\end{itemize}
\end{frame}

@@

\begin{frame}{Types of occupancy models}
	\begin{itemize}
		\item Single species, single season
		\item Na\"ive occupancy: proportion of sites found to be occupied
		\item Hierarchical models
	\end{itemize}
	\begin{center}
		\resizebox{7cm}{!}{\includegraphics{SimpleHierarchicalModel.pdf}}
	\end{center}
\end{frame}

@@

\begin{frame}{Bayesian vs. likelihood occupancy models}
	\begin{itemize}
		\item Maximum likelihood assumes random sample from large population
		\begin{itemize}
			\item Entire section of river was sampled
		\end{itemize}
		\item Most occupancy models have two random processes- occupancy and 
		detection
		\begin{itemize}
			\item We added false detection and track-laying
			\item Extra parameters made likelihood model complicated
		\end{itemize}
	\end{itemize}
\end{frame}

@@

%This slide for DNR only
\begin{frame}{Bayesian model specifics}
	\begin{itemize}
		\item $\psi,\theta \sim \text{Uniform}(0,1)$
		\item $p[{\text{obs}] \sim \text{Beta}(a,b)$
		\begin{itemize}
			\item $a, b \sim \text{Gamma}(1,0.1)$
			\item E similar
			\item $p$ and $E$ had restricted distributions
		\end{itemize}
		\item Burn-in period 10,000 iterations
		\item Covariates: observer, days since snow
	\end{itemize}
\end{frame}

\begin{frame}{Testing the model- data simulations}
	\begin{itemize}
		\item Simulated data with known $\psi$, $\theta$, $p$, $E$.
		\item To simplify, every observer flew every day, flights ran all 
		three days after a snow event
		\item Ran data on our model
		\item When regularity restriction lifted, similar results
	\end{itemize}
\end{frame}

>>>>

\begin{document}
{
	\usebackgroundtemplate{
	\includegraphics[width=\paperwidth]{ottertracks1.jpg}}
	\begin{frame}
		\titlepage
	\end{frame}
}

\begin{frame}{Outline}
	\tableofcontents[pausesections]
\end{frame}

@@

{
	\usebackgroundtemplate{
	\includegraphics[width=\paperwidth]{SnowTracks12.jpg}}
	\begin{frame}{}
	\end{frame}
}

{
	\usebackgroundtemplate{
	\includegraphics[width=\paperwidth]{SNOWTRACKS9.jpg}}
	\begin{frame}
	\end{frame}
}

\begin{frame}{Issues related to data}
	\begin{itemize}
		\item Tracks near plot boundary can be assigned to different plots
		\item Track in one site means more likely to be track in neighboring
		site -- not independent
	\end{itemize}
\end{frame}

@@

\begin{frame}{Types of occupancy models}
	\begin{itemize}
		\item Single species, single season
		\item Na\"ive occupancy: proportion of sites found to be occupied
		\item Hierarchical models
	\end{itemize}
	\begin{center}
		\resizebox{7cm}{!}{\includegraphics{../SimpleHierarchicalModel.pdf}}
	\end{center}
\end{frame}

@@

\begin{frame}{Bayesian vs. likelihood occupancy models}
	\begin{itemize}
		\item Maximum likelihood assumes random sample from large population
		\begin{itemize}
			\item Entire section of river was sampled
		\end{itemize}
		\item Most occupancy models have two random processes -- occupancy and
		detection
		\begin{itemize}
			\item We added false detection and track-laying
			\item Extra parameters made likelihood model complicated
		\end{itemize}
	\end{itemize}
\end{frame}

@@

%This slide for DNR only
\begin{frame}{Bayesian model specifics}
	\begin{itemize}
		\item $\psi,\theta \sim \text{Uniform}(0,1)$
		\item $p[\text{obs}] \sim \text{Beta}(a,b)$
		\begin{itemize}
			\item $a, b \sim \text{Gamma}(1,0.1)$
			\item E similar
			\item $p$ and $E$ had restricted distributions
		\end{itemize}
		\item Burn-in period 10,000 iterations
		\item Covariates: observer, days since snow
	\end{itemize}
\end{frame}

\begin{frame}{Testing the model -- data simulations}
	\begin{itemize}
		\item Simulated data with known $\psi$, $\theta$, $p$, $E$.
		\item To simplify, every observer flew every day, flights ran all
		three days after a snow event
		\item Ran data on our model
		\item When regularity restriction lifted, similar results
	\end{itemize}
\end{frame}
